### 2022-05-08 sections/strategy_Htautau.tex
addressing Luca's comments to V1.4

The analysis strategy adopted in this FCNC $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
%\subsection{Event categorisation and kinematic reconstruction}
%\label{sec:htautau_reco_cat}
The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions(SRs) based on the number of light leptons,
$\had$ candidates, and on the number of light flavoured jets:
%$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
$t_{\ell}\hadhad$, $t_{\ell}\had$ (1j and 2j), $t_h\lephad$ (2j and 3j), $t_h\hadhad$ (2j and 3j), as shown in Table~\ref{tab:srcr}.

@@

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematic fit and assuming a collinear approximation for the tau decay products.
The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is estimated to be $20~\gev$ from a fit of the mass
distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

>>>>

The analysis strategy adopted in this FCNC $\Htautau$ search is similar to the one used in Refs.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.
%\subsection{Event categorisation and kinematic reconstruction}
%\label{sec:htautau_reco_cat}
The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven signal regions(SRs) based on the number of light leptons,
$\had$ candidates, and on the number of light flavoured jets:
%$t_{\ell}\hadhad$, $t_{\ell}\had$(1j and 2j), $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}. 
$t_{\ell}\hadhad$, $t_{\ell}\had$ (1j and 2j), $t_h\lephad$ (2j and 3j), $t_h\hadhad$ (2j and 3j), as shown in Table~\ref{tab:srcr}.

@@

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematic fit and assuming a collinear approximation for the tau decay products.
The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass ($m_{\text{H}}=125~\gev$) and the
measured $E_{\text{x,y}}^{\text{miss}}$  within their expected resolutions ($\sigma_{E_{\text{x,y}}^{\text{miss}}}$), defined as
\begin{eqnarray}
\begin{array}{ll}
\chi^2 =
\left( \frac{m_{\tau\tau,\text{fit}} - m_{\text{H}}}{\sigma_{\tau\tau}} \right)^2 +
\left( \frac{E_{\text{x,fit}}^{\text{miss}} - E_{\text{x}}^{\text{miss}}}{\sigma_{E_{\text{x}}^{\text{miss}}}} \right)^2
  +\left( \frac{E_{\text{y,fit}}^{\text{miss}} - E_{\text{y}}^{\text{miss}}}{\sigma_{E_{\text{y}}^{\text{miss}}}} \right)^2.
\end{array}
\label{eq:eq1}
\end{eqnarray}

The resolution on the Higgs boson mass ($\sigma_{\tau\tau}$) is estimated to be $20~\gev$ from a fit of the mass
distribution of the simulated  $tqH$ signal events, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

### 2022-05-08 sections/systematic_uncertainties.tex
update to V1.3
addressing Luca's comments to V1.4

The $h_{\mathrm{damp}}$ parameter (which controls the amount of radiation produced by the parton shower in
POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with $h_{\mathrm{damp}}$=3$m_t$. The
difference between two samples is treated as one of the systematics as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.

@@

The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
evaluation of the fake factors in the CRtt's are considered and treated as fully correlated in the fit.
The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
its statistical fluctuation and the differences between the leptonic channels.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
%The uncertainties on the MC modelling of the various processes used for
%evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.

@@

Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken from the measured values in Ref.~\cite{Zyla:2020zbs}.
%into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.

>>>>

The $h_{\mathrm{damp}}$ parameter (which controls the amount of radiation produced by the parton shower in
POWHEG-BOX v2) is set to 1.5$m_t$ in the nominal case. Alternative samples are generated with $h_{\mathrm{damp}}$=3$m_t$. The
difference between two samples is treated as a systematic named as ``$t\bar{t}$ $h_{\mathrm{damp}}$''. 
%The uncertainty associated with the choice of NLO generator is derived by comparing the nominal prediction from
%{\powheg}+{\pythiaeight} with a prediction from \textsc{Sherpa}~2.2.1. For the latter, the matrix-element calculation is performed 
%for up to two partons at NLO and up to four partons at LO using \textsc{Comix} and \textsc{OpenLoops}, and
%merged with the {\sherpa} parton shower using the ME+PS@NLO prescription.

@@

The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for
different fake tau sources and different $\pt$ slices. The uncertainties on the MC modelling of the various processes used for
evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.
The uncertainty of the ABCD method is applied on the normalisation factors for muon and electron respectively including both,
its statistical fluctuation and the differences in the normalisation factors between the leptonic channels.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
%The uncertainties on the MC modelling of the various processes used for
%evaluation of the fake factors in the CRtt's are treated as fully correlated in the fit.

@@

Several normalisation and shape uncertainties are taken into account and are treated as fully correlated for the $\Hq$ and $pp\to tH$ signals.
Uncertainties of the Higgs boson branching ratios are taken
%from the measured values in Ref.~\cite{Zyla:2020zbs}.
into account following the recommendation in Ref.~\cite{deFlorian:2016spz}.
The uncertainty of ISR, FSR, scale and PDF are considered and are treated fully correlated in all SRs. The parton shower uncertainties are estimated by comparing
the nominal to an alternative sample interfaced with {\herwig7}.
%the predictions from {\powheg} interfaced either to {\pythiaeight} or {\herwig7}. 
%treated correlatedly with $\ttbar$ samples.
